Summary Tables

### 2022-10-11 summary_tables.Rmd
Adjust for four scenarios. Ref #

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
library(data.table)
})

@@

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
NSCEN <- 3
#cities <- c('accra','sao_paulo','buenos_aires')

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    # scenario == "Scenario 1" ~ "PED_SC", 
    # scenario == "Scenario 2" ~ "CYC_SC",
    # scenario == "Scenario 3" ~ "CAR_SC",
    # scenario == "Scenario 4" ~ "MOT_SC",
    # scenario == "Scenario 5" ~ "BUS_SC",
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

@@

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('ap',as.character(x))))
pa_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('pa',as.character(x))))

sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}

scen_names <- rownames(scen_prop)

#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

### Change in YLLs per 100,000 {#change_YLL_age_100k}
```{r scen_prop = "asis"}
pop_by_age <- lapply(io[-2], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],NSCEN,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = NSCEN)*100000
        )
  )

names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- scen_names
  temp
})

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,NSCEN,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = NSCEN) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_cols[seq(y, length(pa_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})

sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_cols[seq(y, length(ap_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],NSCEN,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = NSCEN) * 100000)
  )

names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")
```

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = NSCEN) * 100000))

names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

@@

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:NSCEN,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_deaths_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = NSCEN)*100000))

names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_ylls_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

@@

    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv", 
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv", 
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv", 
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv", 
            row.names = F)

>>>>

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
library(data.table)
library(writexl)
})

options(dplyr.summarise.inform = FALSE)

@@

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
NSCEN <- 4
#cities <- c('accra','sao_paulo','buenos_aires')

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    # scenario == "Scenario 1" ~ "PED_SC", 
    # scenario == "Scenario 2" ~ "CYC_SC",
    # scenario == "Scenario 3" ~ "CAR_SC",
    # scenario == "Scenario 4" ~ "MOT_SC",
    # scenario == "Scenario 5" ~ "BUS_SC",
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Scenario 4" ~ "MOT_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

@@

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
ap_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
pa_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
pa_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
scen_names <- rownames(scen_prop)
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

@@

### Change in YLLs per 100,000 {#change_YLL_age_100k}
```{r scen_prop = "asis"}
pop_by_age <- lapply(io[-2], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )
yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],NSCEN,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = NSCEN)*100000
        )
  )
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- scen_names
  temp
})
yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,NSCEN,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = NSCEN) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_yll_cols[seq(y, length(pa_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_yll_cols[seq(y, length(ap_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],NSCEN,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = NSCEN) * 100000)
  )
names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")
```

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = NSCEN) * 100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

@@

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_deaths_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = NSCEN)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_ylls_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

@@

    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure
# # Export deaths HB
# path_deaths_wb <- "results/multi_city/health_impacts/Deaths.xlsx"
# deaths_wb <- readWorkbook(path_deaths_wb)
# wb <-  loadWorkbook(path_deaths_wb)
# removeTable(wb = wb, sheet = "Deaths", table = "Tabla1")
# writeDataTable(wb, sheet = "Deaths", x = rbindlist(health$deaths$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "Deaths_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "Deaths_Pathway", x = rbindlist(health$deaths$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_deaths_wb, overwrite =TRUE)
# 
# # Export ylls HB
# path_ylls_wb <- "results/multi_city/health_impacts/YLLs.xlsx"
# ylls_wb <- readWorkbook(path_ylls_wb)
# wb <-  loadWorkbook(path_ylls_wb)
# removeTable(wb = wb, sheet = "YLLs", table = "Tabla1")
# writeDataTable(wb, sheet = "YLLs", x = rbindlist(health$ylls$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "YLLs_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "YLLs_Pathway", x = rbindlist(health$ylls$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_ylls_wb, overwrite =TRUE)
# # Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls_hb_lng = rbindlist(health$ylls$hb, use.names = T),
                         ylls_pathway_hb_lng = rbindlist(health$ylls$pathway_hb, use.names = T),
                         Deaths = rbindlist(health$deaths$hb, use.names = T),
                         Deaths_Pathway = rbindlist(health$deaths$pathway_hb, use.names = T)), path = output_file)

# Export ylls HB
write.csv(rbindlist(health$ylls$hb, use.names = T),
            "results/multi_city/health_impacts/ylls_hb_lng.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(rbindlist(health$ylls$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/ylls_pathway_hb_lng.csv",
            row.names = F)
# Export deaths HB
write.csv(rbindlist(health$deaths$hb, use.names = T),
            "results/multi_city/health_impacts/deaths_hb_lng.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(rbindlist(health$deaths$pathway_hb, use.names = T),
            "results/multi_city/health_impacts/deaths_pathway_hb_lng.csv",
            row.names = F)
```

## PA dist
```{r}
### pa distr
cities <- names(io)[!names(io) %in% 'scen_prop']
l <- list()
for (city in cities){

  # city <- "antofagasta"

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

  l[[city]] <- plyr::rbind.fill(td, td1)

}
write_csv(data.table::rbindlist(l), "results/multi_city/PA/pa_distr.csv")
```
